Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-10 main_paper.tex
Fix a typo in the proof of theorem 2
Small typo on section 5

In 1965, the Head Start program was established to help poor children age three
to five and their families. The program elements include parent involvement,
nutrition, social services, mental health services and health services. To
promote this program in the most needing area, the Office of Economic
Opportunity provided grant-writing assistance to the poorest 300 counties in the
United States based on the 1960 poverty rate. So the poverty rate of the 300th
poorest county serves as a sharp cutoff of treatment. It is shown in
\cite{ludwig2007} that the 228 ``treatment'' counties with poverty rates 10
percentage points above this cutoff have average Head Start spending per
four-year-old as twice of that for 349 ``control'' counties with poverty rates
10 percentage points below this cutoff.

@@

Normality also follows standard arguments for the Wild
bootstrap. Conditional on the regressors and residuals,
$\{R(X_i) \hat\varepsilon_i e_i^* \}$ is a sequence of independent and
mean zero random variables for any measurable function $R$, each with
$p$th absolute moment
$\lvert R(X_i) \hat\varepsilon_i \rvert^p \E \lvert e_i^*
\rvert^{p}$.
The result then holds as a consequence of the Lindeberg-Feller CLT if
we establish that Liapunov's condition holds in probability, specifically that
\begin{equation}\label{eq:17}
  (\tfrac{m}{n})^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
  \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
\end{equation}
with
\begin{equation*}
  R_\bullet(X_i) = \gamma_1 r_1(X_i/h) K_{\bullet,h}(X_i) + h^2 \gamma_2 r_2(X_i/b) K_{\bullet,b}(X_i)
\end{equation*}
for arbitrary nonzero vectors $\gamma_1'$ and $\gamma_2$.
\citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
But similar arguments to those used for the variance establish~\eqref{eq:17}
and complete the proof. \qed

>>>>

In 1965, the Head Start program was established to help poor children aged three
to five and their families. The program elements include parent involvement,
nutrition, social services, mental health services and health services. To
promote this program in the most needing area, the Office of Economic
Opportunity provided grant-writing assistance to the poorest 300 counties in the
United States based on the 1960 poverty rate. So the poverty rate of the 300th
poorest county serves as a sharp cutoff of treatment. It is shown in
\cite{ludwig2007} that the 228 ``treatment'' counties with poverty rates 10
percentage points above this cutoff have average Head Start spending per
four-year-old as twice of that for 349 ``control'' counties with poverty rates
10 percentage points below this cutoff.

@@

Normality also follows standard arguments for the Wild
bootstrap. Conditional on the regressors and residuals,
$\{R(X_i) \hat\varepsilon_i e_i^* \}$ is a sequence of independent and
mean zero random variables for any measurable function $R$, each with
$p$th absolute moment
$\lvert R(X_i) \hat\varepsilon_i \rvert^p \E \lvert e_i^*
\rvert^{p}$.
The result then holds as a consequence of the Lindeberg-Feller CLT if
we establish that Liapunov's condition holds in probability, specifically that
\begin{equation}\label{eq:17}
  (\tfrac{m}{n})^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
  \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
\end{equation}
with
\begin{equation*}
  R_\bullet(X_i) = \gamma_1 r_1(X_i/h) K_{\bullet,h}(X_i) + h^2 \gamma_2 r_2(X_i/b) K_{\bullet,b}(X_i)
\end{equation*}
for arbitrary nonzero vectors $\gamma_1$ and $\gamma_2$.
\citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
But similar arguments to those used for the variance establish~\eqref{eq:17}
and complete the proof. \qed
